Ceph Parallel File System Evaluation Report

### 2013-08-22 abstract.tex
some more minor changes to the abstract

In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
technology for future high-performance computing (HPC) environments.  This
paper presents our evaluation methodology, experiments, results and
observations from mostly parallel I/O performance and scalability
perspectives.  Our work made two unique contributions. First, our evaluation
is performed under a realistic setup for a large-scale capability HPC
environment like ours using a commercial high-end storage system (Data Direct
Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability,
and performance. These changes should also benefit both Ceph and HPC community
at large. Throughout the evaluation, we observed that Ceph still is an
evolving technology under fast-paced development and showing with great
promises.

>>>>

In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
technology for high-performance computing (HPC) environments.  This paper
presents our evaluation methodology, experiments, results and observations from
mostly parallel I/O performance and scalability perspectives.  Our work made
two unique contributions. First, our evaluation is performed under a realistic
setup for a large-scale capability HPC environment like ours using a commercial
high-end storage system.
% (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should also benefit both Ceph and HPC communities at
large. Throughout the evaluation, we observed that Ceph still is an evolving
technology under fast-paced development and showing with great promises.
